The Chemistry Development Kit (CDK): atom typing, rendering, molecular formulas, and substructure searching

### 2016-10-05 article.tex
More small tweaks

The growth of open source software over the last 10 years is evidence           % add REF?
of the ability of communities of developers to develop systems and
processes that lead to high quality software systems for long term
use. The CDK is no different. The adoption of automatic build systems
and quality control methodologies such as unit testing, automated
source code validation, and peer review by fellow developers have
greatly improved the stability of the library. While it has slowed
development somewhat, it has allowed for cleaning up interdependencies
between modules of functionality, and importantly, has improved the scalability
of the development model.  This has resulted in significant new
functionality in core APIs while maintaining the quality of code
depending on those core APIs.

@@

In this section we described the specifics of new APIs and
improvements to pre-existing methods that are available in the latest
CDK.  We then discuss how we have improved and formalized the
development model for the project using unit testing, code review and
guidelines for handling version control. Finally we report on the
availability of binary distributions of the library, allowing users to
include specific modules (and their dependencies) of the CDK in their
own projects (as opposed to developers who work on the CDK library
itself).

@@

We here outline various new and improved APIs in the CDK library since the two previous
publications (corresponding to version XXX)

@@

  Atom type perception is a core cheminformations functionality: the
  atom types describe chemical features of atoms, such as the number
  of neighbors, possible formal charges, (approximate) hybridization,
  electron distribution over orbitals and so on. However, previous
  versions of the CDK implemented atom type perception as part of
  different algorithms, resulting in duplicated and sometimes
  divergent typing schemes. As a result it was cumbersome to add new
  atom types and implement support for new charged and radical species
  in a consistent manner.

>>>>

The growth of open source software over the last 10 years is evidence           % add REF?
of the ability of communities of developers to develop systems and
processes that lead to high quality software systems for long term
use. The CDK is no different. The adoption of automatic build systems
and quality control methodologies such as unit testing, automated
source code validation, and peer review by fellow developers have
greatly improved the stability of the library. While it has slowed
development somewhat, it has allowed for cleaning up interdependencies
between modules of functionality, and importantly, has improved the scalability
of the development model.  This has resulted in significant new
functionality in core application programming interfaces (APIs)
while maintaining the quality of code depending on those core APIs.

@@

This section describes the specifics of new APIs and
improvements to pre-existing methods that are available in the latest
CDK.  We then discuss how we have improved and formalized the
development model for the project using unit testing, code review and
guidelines for handling version control. Finally we report on the
availability of binary distributions of the library, allowing users to
include specific modules (and their dependencies) of the CDK in their
own projects (as opposed to developers who work on the CDK library
itself).

@@

We here outline various new and improved APIs in the CDK library since the two previous
publications (corresponding to version XXX).                                    % FIXME !!!!

@@

  Atom type perception is core cheminformations functionality: the
  atom types describe chemical features of atoms, such as the number
  of neighbors, possible formal charges, (approximate) hybridization,
  electron distribution over orbitals and so on. However, previous
  versions of the CDK implemented atom type perception as part of
  different algorithms, resulting in duplicated and sometimes
  divergent typing schemes. As a result it was cumbersome to add new
  atom types and implement support for new charged and radical species
  in a consistent manner.
